\documentclass[line,margin]{res}

% Margins
\topmargin -0.5in
\textheight 10.0in

% Font
\usepackage{helvetica}

\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{breakurl}
\hypersetup{pdftitle={Hatem Nassrat - Resume} }

%% uncomment for page number
%\pagestyle{plain}

\begin{document}

\name{Hatem A. Nassrat}
% \address used twice to have two lines of address
\address{3139 Veith Street, Halifax, NS B3K 3G9}
\address{(902) 800-5288}


\begin{resume}

\section{OBJECTIVE}
    A position in the field of computers with special
    interests in database development {\&} integration,
    information retrieval {\&} processing, and the ability to
    research {\&} innovate in the various fields of computer
    science.

% \sl will be bold italic in New Century Schoolbook (or
% any postscript font) and just slanted in
% Computer Modern (default) font

\section{EDUCATION}
    {\sl Masters of Applied Computer Science} \hfill May 2009\\
        Dalhousie University \hfill Halifax, NS\\
        Concentration: Data Representation, Databases,
        Web Interfaces.  \medskip
    \newline
    {\sl Bachelor of Computer Science} \hfill May 2006\\
        Dalhousie University \hfill Halifax, NS

\section{CURRENT CERTIFICATIONS}
    {\sl Red Hat Certified Engineer} \hfill Nov 2009\\
        Red Hat Enterprise Linux 5 \hfill 805009562043883\\

\section{PROFILES}
    \href{http://careers.stackoverflow.com/hatem}{Careers},
    \href{https://github.com/pykler/}{GitHub} (\href{http://pykler.github.io/}{Jekyll}),
    \href{https://coderwall.com/pykler}{Coderwall},
    \href{http://stackexchange.com/users/385316/pykler}{StackOverflow},
    \href{https://www.ohloh.net/accounts/pykler}{OhLoh},
    \href{http://ca.linkedin.com/in/pykler/}{LinkedIn},
    \\
    \href{http://web.cs.dal.ca/~nassrat/hatem-nassrat.html}{Dalhousie},
    \href{https://twitter.com/pykler}{Twitter @pykler}

\section{COMPUTER \\ SKILLS}
    {\sl Languages \hspace{35pt}}:
     C/++, Python, Perl, HTML, JavaScript, Java, JSP, PHP, SQL.\\
    {\sl Operating Systems }:
     Linux (RedHat, Debian, Arch), BSD, Windows, OS X. \\
    {\sl Architectures \hspace{27pt}}:
     Worked on high performance clusters (HPC) during my stay at \\
     \hspace*{92pt} Dalhousie. Cloud Computing and Virtual Environments.

\section{EXPERIENCE}

    {\sl Co-Founder and CTO} \hfill Sept 2012 - Present \\
    \href{http://www.leadsift.com}{LeadSift} \hfill Halifax, NS \smallskip
    \begin{itemize}  \itemsep -2pt % reduce space between items
     \item Real-time Sifting of Social Media Posts
     \item Classifying and finding intent in short texts
     \item Architecting integrations with third party systems
     \item Architecting solutions for high availability and load
     \item {\bf Technologies:} \hspace{1pt}
        Python, Django, Selenium, HTML/JS, Angular, CoffeeScript, \newline
        \hspace*{72pt} NodeJS, Scala, NLP, Mongo, Postgres, Neo4J, Redis, \newline
        \hspace*{72pt} Git, Mercurial, Unix, Debian, Puppet, ProxMox, ...
    \end{itemize}

    {\sl Chief Technical Officer (CTO)} \hfill March 2011 - Sept 2012 \\
    GenieKnows Inc. (\href{http://www.genieknows.com}{GenieKnows.com}) \hfill Halifax, NS \smallskip
    \begin{itemize}  \itemsep -2pt % reduce space between items
     \item Leading development efforts to meet demanding deadlines
     \item Architecting new developments and developing future roadmaps for the \\
     current platform
     \item Working with IT consultants to create a reliable cloud computing platform \\ to host GenieKnows' applications
     \item {\bf Technologies:} \hspace{1pt}
        Python, Java, HTML/Javascript, JQuery, Django, SVN \newline
        \hspace*{72pt} Unix, CentOS, Cisco ASA / ASDM, ProxMox, Cloud ...
    \end{itemize}

   {\sl Senior Consultant} \hfill April 2008 - March 2011 \\
    NTT Data (Formerly Keane Canada) \hfill Halifax, NS \\
    \href{http://www.pason.com/}{Pason Systems} - Oil {\&} Gas Industry \smallskip
    \begin{itemize}  \itemsep -2pt % reduce space between items
     \item Working in a stressful enterprise production environment
     \item Maintaining unittests and updating QA test plans
     \item Developing ReSTful services, to acheive Service Oriented Architecture
     \item Working with multiple programming languages
            simultaneously, while \\ maintaining integration.
     \item {\bf Technologies:} \hspace{1pt}
        C, Java, HTML/Javascript, Prototype, Dojo, Python, Pylons, \newline
        \hspace*{72pt} XML, JSON, SVN, Git, MVC, ReST, SOA, Unix, CentOS.
    \end{itemize}

\newpage
\opening

   {\sl Software Engineer} \hfill Sept 2007 - April 2008 \\
    IT Interactive Service (\href{http://www.genieknows.com}{GenieKnows.com}) \hfill Halifax, NS \\
    Research {\&} Development Department \smallskip
    \begin{itemize}  \itemsep -2pt % reduce space between items
     \item Developed interface functionality for
             local.genieknows.com (now \href{http://www.yellowee.com}{Yellowee.com})
     \item Developed back end modules for the search
             engines developed by
             \href{http://www.genieknows.com}{GenieKnows.com}
     \item Investigated various research topics
             in the fields of information retrieval.
     \item {\bf Technologies:} \hspace{1pt}
        Perl, Python, C/++, PHP, Javascript, OSGeo, CentOS, \\
        \hspace*{72pt} Unix, SVN.
    \end{itemize}

   {\sl Web Programmer} \hfill June 2007 - Sept 2007 \\
    ArtistXite.com \hfill Halifax, NS \smallskip
    \begin{itemize}  \itemsep -2pt % reduce space between items
     \item Developed interface and backend functionality to display
               web traffic statistics.
     \item Developed a system to upload videos and encode them
                into flash video format.
     \item {\bf Technologies:}\hspace{4pt}
        MySQL, Perl, PHP, Javascript, FFMpeg, Unix, SVN, CVS.
    \end{itemize}

   {\sl Masters Student} \hfill Aug 2007 - May 2009 \\
     Dalhousie University \hfill Halifax, NS \smallskip
      \begin{itemize}  \itemsep -2pt % reduce space between items
       \item Implemented the
       \href{http://designtheory.org/library/extrep/designdb-1.0.pdf}{DesignDB} (DDB
       project extension) as my Masters Thesis.
       \item Designed and Implemented the
       \href{http://designtheory.org/library/extrep/}{External
       Representation of Block Designs v3}.
%     \end{itemize}
%       \begin{itemize}  \itemsep -2pt % reduce space between items
       \item {\bf Technologies:} \hspace{1pt}
        Python, Python Ctypes, Pylons, SqlAlchemy, Mako, AJAX, \newline
        \hspace*{72pt} JSON, XML, SQLite, PostgreSql, Mercurial Hg,
        (Li$|$U)nix.
    \end{itemize}

    {\sl Python/Web Developer} \hfill June 2006 - Aug 2007 \\
    D-Drive Lab, Dalhousie University FCS \hfill Halifax, NS \\
    \href{http://web.cs.dal.ca/~peter/designdb/}{Design Database Project}\\
    Satellite Project of \href{http://designtheory.org}{DesignTheory.org},
    Queen Mary University \hfill London, UK \smallskip
        \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Developed a python web application that connects to an Sqlite
    database \\ containing statistical designs.
    \item Assisted in the design of a schema to store statistical t-designs.
    \item Used a state of the art pythonic web framework (Cherrypy 3.0),
    along with other, such as a templating language, to develop the design
    database browser.
    \item {\bf Technologies:} \hspace{1pt}
        Python, Cherrypy 3.0, Genshi, HTML, SQLite, XML, \newline
        \hspace*{72pt} Shell (Unix) Scripting, Apache, SVN, Mercurial Hg.
        \end{itemize}

    {\sl Professional Software Developer} \hfill Since 2003 \smallskip
        \begin{itemize}  \itemsep -2pt % reduce space between items
    \item {\bf Technologies:} \hspace{3pt}
        Oracle, Oracle Developer (IDE), Java, Microsoft Excel, \newline
        \hspace*{72pt} J2EE, J2SE, Apache, PHP, MySQL, Apache, IIS, \newline
        \hspace*{72pt} Windows Networking
        \end{itemize}

\section{COMMUNITY \\ SERVICE}
    {\sl IT Committee Lead Member} \hfill Feb 2008 - Jan 2012 \\
    Ummah Masjid (Building Committee) \hfill Halifax, NS \smallskip
        \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Managed a small team to assemble a website in Joomla to inform
    potential donors and members of the community about the state of the
    project.
    \item Designed and implemented a Joomla Template along with new or
    improved joomla plugins that were used in the Masjid Website
    \href{http://www.ummahmasjid.ca}{www.ummahmasjid.ca}.
    \item Prepared presentations, slideshows and media
    required by the committee.
    \item Setup a networked computer lab for the local school (Maritime
    Muslim Academy).
    \item {\bf Technologies:} \hspace{1pt}
        \LaTeX, PHP, Joomla, Windows Networking.
        \end{itemize}

\section{HOBBIES}
    Sports (Everything especially football and basketball), Cars,
    Diving/Snorkelling, \\Electronics, and \LaTeX\ (eg. this resume).

\end{resume}
\end{document}
